An asymptotically normal out-of-sample test of equal predictive accuracy for nested models

### 2012-05-17 Paper.tex
Updated BibTeX references so that paper would compile

\oos\ tests are commonly used in International Macroeconomics,
Macroeconomics, and Finance (see, for example, \citealt{MeR:83};
\citealt{StW:03}; and \citealt{GoW:08}) and there is a substantial
literature developing the theoretical properties of these statistics,
beginning primarily with \citet{DiM:95} and
\citet{Wes:96}.\footnote{Other papers in this literature include
  \citet{WeM:98}, \citet{Mcc:98,Mcc:00},
  \citet{ClM:01,ClM:05-2,ClM:05,ClM:11b,ClM:11,ClM:12},
  \citet{CCS:01}, \citet{CoS:02,CoS:04,CoS:07}, \citet{Whi:00},
  \citet{InK:04,InK:06}, \citet{Han:05}, \citet{Ros:05},
  \citet{ClW:06,ClW:07}, \citet{Ana:07}, \citet{GiR:09,GiR:10},
  \citet{HuW:10}, \citet{HLN:11}, \cite{InR:11}, \cite{Pin:11},
  \cite{RoS:11,RoS:11b}, and \citet{Cal:11}, among others.  For recent
  reviews of this literature and additional references, see
  \citet{McW:02}, \citet{CoS:06}, \citet{Wes:06}, \citet{ClM:11c},
  \citet{CoD:11}, and \citet{Gia:11}} In a pair of papers,
\citet{ClW:06,ClW:07} develop an \oos\ test of the null hypothesis
that a small benchmark model is correctly specified.  Their test
compares the forecasting performance of a pair of nested models, and
the null hypothesis is that the innovations in the smaller model form
a martingale difference sequence.  This test procedure is popular, and
one assumes that this is due in part to the statistic's convenience,
the statistic is approximately normal after adjusting for the
estimation error of the larger model.  Normality comes from a
fixed-length rolling window, as in \citet{GiW:06}, and the adjustment
centers the statistic appropriately.  This statistic is especially
convenient because other \oos\ tests for similar hypotheses
(\citealt{CCS:01}; \citealt{ClM:01,ClM:05}; \citealt{CoS:02,CoS:04};
and \citealt{Mcc:07}; among others) have a nonstandard limit
distribution and place restrictions on the models under consideration,
while other asymptotically normal statistics test a different null
hypothesis \citep{GiW:06} or place assumptions on the models and \dgp\
that are often violated in empirical work (\citealt{DiM:95};
\citealt{Wes:96}; \citealt{WeM:98};
\citealt{Mcc:00}).\footnote{\citet{DiM:95} assume that the models are
  not estimated. \citet{Wes:96}, \citet{WeM:98}, and \citet{Mcc:00}
  implicitly assume that the models do not converge to the same limit,
  which rules out nesting.}

@@

This paper also presents a new result for the validity of block
bootstraps with \oos\ statistics, which is necessary to verify that
the StepM is valid.  Existing results on bootstrapping \oos\
statistics have some drawbacks.  \citet{Whi:00} and \citet{Han:05} use
the stationary bootstrap, but require the test sample to be much
smaller than the training sample, which obviously does not hold here.
\citet{CoS:07} relax that requirement, but make the statistic more
complicated than necessary by adjusting the objective function of the
bootstrapped statistic to center it correctly.\footnote{Their
  recentering is required for consistency and does not imply higher
  order accuracy.}  A parametric bootstrap, such as that used by
\cite{Mar:95}, \cite{Lut:99}, and \citet{ClM:11}, is an alternative
method, but requires the benchmark model to be correctly specified.
Although I focus on the null hypothesis that the benchmark is
correctly specified, this paper's block bootstrap methods remain valid
when the benchmark is misspecified and are relatively easy to
implement.  So this paper's result for bootstrapping \oos\ statistics
considerably improves on existing procedures.

@@

Suppose we have the family of hypotheses, $H_1,\dots,H_J$.  It is
clear that testing each hypothesis individually will often have a
probability greater than the tests' nominal size of rejecting at least
once.\footnote{Unless the statistics used for each test are completely
  interdependent, the probability will be strictly greater than the
  nominal size.}  Econometricians, e.g. \citet{Whi:00},
\citet{Han:05}, \cite{HuW:10}, and \citet{ClM:11}, have emphasized
statistics that test families of hypotheses that control the
probability any hypothesis is rejected given that they all are true,
known as \textit{weak control of familywise error}
(\wfwe).\footnote{An exception is \citet{HHK:10} who combine
  \citepos{RoW:05} StepM with \citepos{Han:05} threshold rule to
  control \sfwe\ for certain families of one-sided tests.}  This paper
focuses instead on controlling the probability that at least one true
hypothesis is rejected given any combination of true and false
hypotheses, known as \textit{strong control of familywise error}
(\sfwe).  For most empirical work, \sfwe\ is desired; fortunately,
even though the papers only prove \wfwe, statistics based on
nonparametric block bootstraps \citep{Whi:00,Han:05} can be shown to
control \sfwe\ as well \citep[this follows directly from][]{RoW:05}
and those based on the parametric bootstrap \citep{ClM:11} essentially
control \sfwe\ if the individual null hypotheses are strengthened
slightly as below (see Part~(\ref{it:1}) of Theorem~\ref{res:2} as
well as Remark~\ref{rem:2}).  \citet{HuW:10} propose that researchers
construct critical values from the asymptotic joint distribution of
the test statistics and can control \sfwe\ as long as there is a
consistent estimator of that distribution.

@@

  The same reasoning implies that a parametric bootstrap
  \citep[i.e.][]{ClM:11} achieves control of \sfwe\ only under the
  stronger hypotheses of Part~(\ref{it:1}).  Fortunately,
  Part~(\ref{it:1}) seems to capture the goals of most empirical work,
  so researchers can make use of the considerable simplifications that
  occur in that setting.
\end{rem}

@@

\section{Monte Carlo Results}\label{sec:2}
I'll conduct two brief Monte Carlo experiments to demonstrate that
this paper's modified version of \citepos{ClW:07} statistic performs
similarly to their original test in the situations they
study.\footnote{All of these simulations were programmed in R
  \citep[version 2.14.0]{R} and use the \textsc{MASS} \citep[version
  info]{VeR:02}, xtable \citep[1.6-0]{Dah:09}, and dbframe
  \citep[version 0.2.1]{Cal:10b} packages.  For details on the
  programming, please see the supplemental appendices
  \citep{Cal:11f,Cal:11g,Cal:11h}.}  I'll use both of the \dgp s they
consider as well as a modification to study the performance of the
statistics if there is instability.

@@

Here, I conduct the same analysis, but using this paper's \mds\ test.
The benchmark model is the excess return's sample mean (as in the
original) and the alternative models are of the form
\[\text{excess return}_{t} = \alpha_{0} + \alpha_{1}\ 
\text{predictor}_{t-1} + \varepsilon_{t},\] where $\alpha_{0}$ and
$\alpha_{1}$ are estimated by \ols\ using a \windowlength-year window.
The predictors used are listed in the ``predictor'' column of
Table~\ref{tab:em1} \citep[see][for a detailed description of the
variables]{GoW:08}.  We also consider \citepos{CaT:08} proposed
correction to the models, that the forecasts be bounded below by zero
since negative forecasts are incredible, as well as two simple
combination forecasts, the mean and the median (over both the original
and the non-negative forecasts).  The data set is annual data
beginning in 1927 and ending in 2009, and the rolling window uses
\windowlength\ observations.\footnote{This statistical analysis was
  conducted in R \citep{R} using the xtable
  \citep[version~1.6-0]{Dah:09}, and dbframe \citep[version
  0.2.5]{Cal:10b} packages; please see the supplemental appendices for
  details on the programming \citep{Cal:11f,Cal:11g,Cal:11h}.}

>>>>

\oos\ tests are commonly used in International Macroeconomics,
Macroeconomics, and Finance (see, for example, \citealt{MeR:83};
\citealt{StW:03}; and \citealt{GoW:08}) and there is a substantial
literature developing the theoretical properties of these statistics,
beginning primarily with \citet{DiM:95} and
\citet{Wes:96}.\footnote{Other papers in this literature include
  \citet{WeM:98}, \citet{Mcc:98,Mcc:00},
  \citet{ClM:01,ClM:05-2,ClM:05,ClM:11b,ClM:12,ClM:12b},
  \citet{CCS:01}, \citet{CoS:02,CoS:04,CoS:07}, \citet{Whi:00},
  \citet{InK:04,InK:06}, \citet{Han:05}, \citet{Ros:05},
  \citet{ClW:06,ClW:07}, \citet{Ana:07}, \citet{GiR:09,GiR:10},
  \citet{HuW:10}, \citet{HLN:11}, \cite{InR:11}, \cite{Pin:11},
  \cite{RoS:11,RoS:11b}, and \citet{Cal:11}, among others.  For recent
  reviews of this literature and additional references, see
  \citet{McW:02}, \citet{CoS:06}, \citet{Wes:06}, \citet{ClM:11c},
  \citet{CoD:11}, and \citet{Gia:11}} In a pair of papers,
\citet{ClW:06,ClW:07} develop an \oos\ test of the null hypothesis
that a small benchmark model is correctly specified.  Their test
compares the forecasting performance of a pair of nested models, and
the null hypothesis is that the innovations in the smaller model form
a martingale difference sequence.  This test procedure is popular, and
one assumes that this is due in part to the statistic's convenience,
the statistic is approximately normal after adjusting for the
estimation error of the larger model.  Normality comes from a
fixed-length rolling window, as in \citet{GiW:06}, and the adjustment
centers the statistic appropriately.  This statistic is especially
convenient because other \oos\ tests for similar hypotheses
(\citealt{CCS:01}; \citealt{ClM:01,ClM:05}; \citealt{CoS:02,CoS:04};
and \citealt{Mcc:07}; among others) have a nonstandard limit
distribution and place restrictions on the models under consideration,
while other asymptotically normal statistics test a different null
hypothesis \citep{GiW:06} or place assumptions on the models and \dgp\
that are often violated in empirical work (\citealt{DiM:95};
\citealt{Wes:96}; \citealt{WeM:98};
\citealt{Mcc:00}).\footnote{\citet{DiM:95} assume that the models are
  not estimated. \citet{Wes:96}, \citet{WeM:98}, and \citet{Mcc:00}
  implicitly assume that the models do not converge to the same limit,
  which rules out nesting.}

@@

This paper also presents a new result for the validity of block
bootstraps with \oos\ statistics, which is necessary to verify that
the StepM is valid.  Existing results on bootstrapping \oos\
statistics have some drawbacks.  \citet{Whi:00} and \citet{Han:05} use
the stationary bootstrap, but require the test sample to be much
smaller than the training sample, which obviously does not hold here.
\citet{CoS:07} relax that requirement, but make the statistic more
complicated than necessary by adjusting the objective function of the
bootstrapped statistic to center it correctly.\footnote{Their
  recentering is required for consistency and does not imply higher
  order accuracy.}  A parametric bootstrap, such as that used by
\cite{Mar:95}, \cite{Lut:99}, and \citet{ClM:12b}, is an alternative
method, but requires the benchmark model to be correctly specified.
Although I focus on the null hypothesis that the benchmark is
correctly specified, this paper's block bootstrap methods remain valid
when the benchmark is misspecified and are relatively easy to
implement.  So this paper's result for bootstrapping \oos\ statistics
considerably improves on existing procedures.

@@

Suppose we have the family of hypotheses, $H_1,\dots,H_J$.  It is
clear that testing each hypothesis individually will often have a
probability greater than the tests' nominal size of rejecting at least
once.\footnote{Unless the statistics used for each test are completely
  interdependent, the probability will be strictly greater than the
  nominal size.}  Econometricians, e.g. \citet{Whi:00},
\citet{Han:05}, \cite{HuW:10}, and \citet{ClM:12b}, have emphasized
statistics that test families of hypotheses that control the
probability any hypothesis is rejected given that they all are true,
known as \textit{weak control of familywise error}
(\wfwe).\footnote{An exception is \citet{HHK:10} who combine
  \citepos{RoW:05} StepM with \citepos{Han:05} threshold rule to
  control \sfwe\ for certain families of one-sided tests.}  This paper
focuses instead on controlling the probability that at least one true
hypothesis is rejected given any combination of true and false
hypotheses, known as \textit{strong control of familywise error}
(\sfwe).  For most empirical work, \sfwe\ is desired; fortunately,
even though the papers only prove \wfwe, statistics based on
nonparametric block bootstraps \citep{Whi:00,Han:05} can be shown to
control \sfwe\ as well \citep[this follows directly from][]{RoW:05}
and those based on the parametric bootstrap \citep{ClM:12b} essentially
control \sfwe\ if the individual null hypotheses are strengthened
slightly as below (see Part~(\ref{it:1}) of Theorem~\ref{res:2} as
well as Remark~\ref{rem:2}).  \citet{HuW:10} propose that researchers
construct critical values from the asymptotic joint distribution of
the test statistics and can control \sfwe\ as long as there is a
consistent estimator of that distribution.

@@

  The same reasoning implies that a parametric bootstrap
  \citep[i.e.][]{ClM:12b} achieves control of \sfwe\ only under the
  stronger hypotheses of Part~(\ref{it:1}).  Fortunately,
  Part~(\ref{it:1}) seems to capture the goals of most empirical work,
  so researchers can make use of the considerable simplifications that
  occur in that setting.
\end{rem}

@@

\section{Monte Carlo Results}\label{sec:2}
I'll conduct two brief Monte Carlo experiments to demonstrate that
this paper's modified version of \citepos{ClW:07} statistic performs
similarly to their original test in the situations they
study.\footnote{All of these simulations were programmed in R
  \citep[version 2.14.0]{R} and use the \textsc{MASS} \citep[version
  info]{VeR:02}, xtable \citep[1.6-0]{Dah:09}, and dbframe
  \citep[version 0.2.1]{Cal:10b} packages.  For details on the
  programming, please see the supplemental appendix \citep{Cal:11f}.}
I'll use both of the \dgp s they consider as well as a modification to
study the performance of the statistics if there is instability.

@@

Here, I conduct the same analysis, but using this paper's \mds\ test.
The benchmark model is the excess return's sample mean (as in the
original) and the alternative models are of the form
\[\text{excess return}_{t} = \alpha_{0} + \alpha_{1}\ 
\text{predictor}_{t-1} + \varepsilon_{t},\] where $\alpha_{0}$ and
$\alpha_{1}$ are estimated by \ols\ using a \windowlength-year window.
The predictors used are listed in the ``predictor'' column of
Table~\ref{tab:em1} \citep[see][for a detailed description of the
variables]{GoW:08}.  We also consider \citepos{CaT:08} proposed
correction to the models, that the forecasts be bounded below by zero
since negative forecasts are incredible, as well as two simple
combination forecasts, the mean and the median (over both the original
and the non-negative forecasts).  The data set is annual data
beginning in 1927 and ending in 2009, and the rolling window uses
\windowlength\ observations.\footnote{This statistical analysis was
  conducted in R \citep{R} using the xtable
  \citep[version~1.6-0]{Dah:09}, and dbframe \citep[version
  0.2.5]{Cal:10b} packages; please see the supplemental appendices for
  details on the programming \citep{Cal:11f}.}
